---
title: "p8105 Homework 1"
author: Yuanming Mao
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

Creates a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod","mod","mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the means of numbers and logical but not character or factor.

```{r}

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

The logic vector is converted to numeric 0 and 1, the character vector is converted to NA for all elements, and the factor vector is converted to numeric. 
It helps explain that R regards true as 1 and false as 0 automatically. And it shows that a factor vector can be converted to numeric, but a character vector cannot.

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```



## Problem 2

