---
title: "p8105 Homework 1"
author: Yuanming Mao
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod","mod","mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the means of numbers and logical but not character or factor.

```{r}

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

The logic vector is converted to numeric 0 and 1, the character vector is converted to NA for all elements, and the factor vector is converted to numeric. 
It helps explain that R regards true as 1 and false as 0 automatically. And it shows that a factor vector can be converted to numeric, but a character vector cannot.

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")

summary(penguins)
```

This dataset includes data of location and physical features of 3 species of penguins. Important variables include species, island where the penguin is from, bill length and depth in mm, flipper length in mm, body mass in gram, sex, and year. Three penguins species include Adelie, Chinstrap and Gentoo. Three islands that these penguins are from include Biscoe, Dream, and Torgersen.Bill length ranges from 32.10 to 59.60 mm, bill depth from 13.10 to 21.50 mm, flipper length from 172.0 to 231.0 mm, and body mass from 2700 to 6300 grams.

This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length of those penguins is `r mean(pull(penguins,flipper_length_mm),na.rm=TRUE)` mm.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf",height=4,width=4)
```



